The `forestecology` R package for modeling interspecies competition between trees

### 2021-02-02 etc/paper/forestecology.Rmd
Changed title

---
title: "`forestecology` package for modeling interspecies competition between trees"

@@

```{r bw-model-rmse}
predictions %>%
  yardstick::rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

---
title: "The `forestecology` R package for modeling interspecies competition between trees"

@@

```{r bw-model-rmse}
predictions %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```
